A Horrocks-type theorem for orthogonal $K_2$

### 2019-08-19 dl-paper.tex
Rewritten stuff

\title{On the presentation of orthogonal groups over polynomial rings}
\keywords {Steinberg group, $K_2$-functor, Serre problem
 {\em Mathematical Subject Classification (2010):} 19C20}
\author{Andrei Lavrenov}
\address{Mathematisches Institut der Universit\"at M\"unchen, Theresienstr. 39, D-80333 M\"unchen}
\email{avlavrenov at gmail.com}

@@

\section{Preliminaries}
$\langle \alpha, \beta \rangle = (\alpha, \beta^\vee) = (\alpha, \frac{2\beta}{(\beta, \beta)})$
Our convention for Cartan matrices is 
$A_{ij} = \langle \alpha_i, \alpha_j \rangle = (\alpha_i, \alpha_j^\vee)$.

\subsection{Steinberg groups}
Let $\Phi$ be a reduced and irreducible root system of rank $\geq 2$ and $R$ be a commutative ring with $1$. Recall that in this case the \emph{Steinberg group} $\St(\Phi, R)$ can be defined by means of generators $x_{\alpha}(s)$ (where $\alpha\in\Phi, s\in R$) and relations:
\begin{align}
& \phantom{[}
x_\alpha(s) \cdot x_\alpha(t) = x_\alpha(s+t),\ \alpha\in\Phi,\ s,t\in R; \label{rel:add}\\
& [x_\alpha(s), x_\beta(t)] = \prod\limits_{i,j\in\mathbb{N}}
 x_{i\alpha + j\beta}\left(N_{\alpha,\beta ij}\, s^i t^j\right),\quad \alpha,\beta\in\Phi,\ \alpha\neq\pm\beta,\ s,t\in R. \label{rel:CCF}
\end{align}
The indices $i$, $j$ appearing in the right-hand side of the above relation range over
all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
The constants $N_{\alpha \beta i j}$ appearing in the right-hand side of \eqref{rel:CCF} are integers equal to $\pm 1,\pm 2,\pm 3$, they are called the {\it structure constants} of the Chevalley group $G_{sc}(\Phi, R)$. Several different methods have been proposed for choosing signs of these constants, see e.\,g.~\cite{V00}, \cite[\S~9]{VP}.

Whenever we speak of the Steinberg group $\St(\Psi, R)$ parametrized by a root subsystem $\Psi \subset \Phi$ we imply that the choice of structure constants 
 for $\St(\Psi, R)$ is compatible with that for $\St(\Phi, R)$ (i.\,e. the obvious map between these groups induced $\Psi\subseteq \Phi$ is well-defined).

In this paper we will be mostly interested in the case when the Dynkin diagram of $\Phi$ is {\it simply-laced}, i.\,e. does not contain double bonds. In this case the defining relations of $\St(\Phi, R)$ have the following simpler form:
\begin{align}
&x_{\alpha}(a)\cdot x_{\alpha}(b)=x_{\alpha}(a+b), \tag{R1}\\
&[x_{\alpha}(a),\,x_{\beta}(b)]=x_{\alpha+\beta}(N_{\alpha\beta} \cdot ab),\text{ for }\alpha+\beta\in\Phi, \tag{R2} \\
&[x_{\alpha}(a),\,x_{\beta}(b)]=1,\text{ for }\alpha+\beta\not\in\Phi\cup0. \tag{R3}
\end{align}
In the above formulae $a, b \in R$ and the integers $N_{\alpha, \beta} = N_{\alpha, \beta, 1, 1} = \pm 1$ are the structure constants of the Lie algebra of type $\Phi$. Although there is still some degree of freedom in their choice, these constants always must satisfy the relations, provided by the following lemma (cf.~\cite[\S~14]{VP}).
\begin{lemma} Suppose $\Phi$ is simply laced and $\alpha, \beta$ are roots of $\Phi$ such that $\alpha+\beta\in \Phi$, then holds
\begin{equation} \label{eq:simplest} N_{\alpha, \beta} = -N_{\beta,\alpha} = - N_{-\alpha, -\beta} = N_{\beta, -\alpha-\beta} = N_{-\alpha-\beta, \alpha}. \end{equation}
If, moreover, $\gamma \in \Phi$ is such that $\alpha,\beta,\gamma$ form a basis of a root subsystem of type $\rA_3$ then holds
\begin{equation} \label{eq:cocycle} N_{\beta,\gamma} \cdot N_{\alpha, \beta+\gamma} = N_{\alpha+\beta, \gamma} \cdot N_{\alpha, \beta}. \end{equation} \end{lemma}
In the computations below we use identities~\eqref{eq:simplest} without explicit reference.

@@

\subsection{\texorpdfstring{$\K_2$}{K2}-groups and symbols} In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}. Notice that our treatment of symbols follows~\cite{DS73}. Recall that Steinberg symbols are defined for arbitrary $s, t \in R^\times$ as follows:
\begin{equation} \label{eq:steinberg} \{ s, t \}_\alpha = h_\alpha(st) \cdot h_\alpha^{-1}(s) \cdot h_\alpha^{-1}(t). \end{equation}
In turn, Dennis--Stein symbols are defined for arbitrary $a, b\in R$ satisfying $1 + ab \in R^\times$:
\begin{equation} \label{eq:dennis-stein}  \langle a,b \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- b}{1 + ab}\right) \cdot x_{\alpha}(a) \cdot x_{-\alpha}(b) \cdot x_{\alpha}\left(\tfrac{- a}{1+ab}\right) \cdot h_{\alpha}^{-1}(1 + ab). \end{equation} 
Dennis--Stein symbol $\langle a, b \rangle_\alpha$ can be expressed through Steinberg symbols in the special case when either $a$ or $b$ is an invertible element of $R$. More specifically, the following formulae hold (cf.~\cite[p.~250]{DS73}).
\begin{equation} \label{DS-S-relationship} \langle a, b \rangle_\alpha = \{-a, 1+ab\}_\alpha\text{ for } a, 1+ab\in R^\times,\ \
 \{ s, t \}_\alpha = \left\langle -s, \tfrac{1 - t}{s} \right\rangle_\alpha\text{ for } s, t\in R^\times. \end{equation}
%Using~\eqref{eq:conj-h-h} it is easy to verify that \[[h_\alpha(s), h_\beta(t)] = \{s, t^{\langle \alpha, \beta \rangle}\}_\alpha = \{t, s^{\langle \beta, \alpha \rangle}\}_\beta^{-1}.\] 
Steinberg and Dennis--Stein symbols depend only on the length of $\alpha$, in particular they do not depend on $\alpha$ if $\Phi$ is simply-laced. If $\Phi$ happens to be {\it nonsymplectic}, i.\,e. $\Phi \neq \rA_1, \rB_2, \rC_{\geq 3}$, Steinberg symbols are antisymmetric and bimultiplicative, i.\,e. they satisfy the following identities: \begin{equation} \label{eq:symbol-properties} \{ u, st \} = \{ u, s\} \{ u, t \}, \ \{ u, v \} = \{ v, u\}^{-1}. \end{equation}
For these and other properties of symbols we refer the reader to~\cite{DS73}.

@@

\subsection{Relative Steinberg groups and unstable K-groups} \label{sec:quillen}
In this subsection we recall the definitions and basic facts pertaining to relative Steinberg groups as defined by J.-L.~Loday in~\cite{Lo78}, where a theory of relative central extensions was developed and then applied to the stable Steinberg group $\St(R)$ from algebraic K-theory. The main goal of this subsection is to show that Loday's results can be applied to unstable Steinberg groups, and that the resulting relative groups enjoy many good properties of their stable counterparts.
Some of the results of this subsection have been briefly mentioned in~\cite{S15} (cf. e.\,g. Corollaries 3--4).

@@

Now let us give the example of a triple $(G, P, S)$ playing a key role in the present paper.
We denote by $\mathrm{O}_{2n}(R)$ and $\mathrm{EO}_{2n}(R)$ the orthogonal group of rank $n$ over a ring $R$ and its elementary subgroup, respectively
 (see e.\,g.~\cite{Su82} for the definition of these groups).
Now set $G_n = \mathrm{O}_{2n}(-)$, $P_n = \mathrm{EO}_{2n}(R)$, $S_n = \St(\rD_n, -)$ and let $\pi$ be the obvious projection $S_n \to P_n$.

@@

\section{Proof of the first part of the injectivity theorem} \label{firstPart}
We start this section by recalling basic notation and facts pertaining to hermitian K-theory.
First of all, recall that the stable orthogonal K-groups $\KO_i(R) = \KO_i(\infty, R)$ are precisely the hermitian K-groups ${}_{-1}\!L_i(R)$ introduced by Karoubi in~\cite{Ka80}. We will need yet another redesignation for these groups $\KO_i(R)$, which comes from the theory of {\it higher Grothendieck--Witt groups of schemes}.
Recall that this theory, developed by M.~Schlichting, is a modern broad generalization of the classical hermitian K-theory of rings developed in~\cite{Ka80}.
We refer the reader to~\cite[\S~2]{FRS12} and~\cite[\S~2]{AF17} for the introduction to it.

For our purposes it suffices to restrict attention to the affine case, in which we can consider Grothendieck--Witt groups $\GW_i^{[k]}(R)$ for $i \geq 1,\ [k] \in \ZZ/4\ZZ$
 simply as a shorthand for the following groups
\begin{equation*} \GW_i^{[k]}(R) = \left\{\begin{array}{ll} \KO_i(R), & k = 0 \\ U_i(R), & k = 1 \\ \mathrm{KSp}_i(R), & k = 2 \\ {}_{-1}\!U_i(R), & k = 3. \end{array}\right. \end{equation*}
The groups ${}_{\pm 1}\!U_i(R)$, $\mathrm{KSp}_i(R)$ are defined in~\cite{Ka80} and we will not use their definition. 
What we need from Grothendieck--Witt groups is the following result due to M.~Schlichting.
\begin{theorem*}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $R$ is a regular ring such that $2 \in R^*$, 
then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{theorem*}
\begin{proof} This is a very special case of~\cite[Theorem~9.13]{Sch16} and the remark that follows it. \end{proof}
We will use the above theorem only in the special case $i=0$, in which it boils down to an earlier result of Hornbostel, see~\cite[Corollary~5.3]{Ho05}.

@@

It is obvious that $K(A[X], M[X])$ contains the subgroup $\overline{\St}(\Phi, A[X], XM[X])$. It turns out that although being larger than this subgroup, $K(A[X], M[X])$ contains very few extra generators, which can all be explicitly described.

Since $ev_{X=0}^*$ admits a section, we can consider $\overline{\St}(\Phi, A, M)$ and $\St(\Phi, M)$ as subgroups of $\overline{\St}(\Phi, A[X], M[X])$,
 moreover, one has $\overline{\St}(\Phi, A[X], M[X]) = \overline{\St}(\Phi, A, M) \cdot K(A[X], M[X]).$
\begin{lemma} The following decomposition holds
 \[ K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right].\] \end{lemma}
\begin{proof} Fix $g \in K(A[X], M[X])$ and write it as $g(X) = \prod_i z_{\alpha_i}(f_i(X), \xi_i(X))$ for some $f_i(X) = f_i(0) + Xf_i'(X) \in M[X]$, $\xi_i(X) = \xi_i(0) + X\xi_i'(X) \in A[X]$.
 It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the element $g(X)$ is congruent to $g_1(X) = \prod_i z_{\alpha_i}(f_i(0), \xi_i(X)).$

>>>>

\title{A Horrocks-type theorem for orthogonal $K_2$}
\keywords {Steinberg group, $K_2$-functor, Serre problem
 {\em Mathematical Subject Classification (2010):} 19C20}
\author{Andrei Lavrenov}
\address{Mathematisches Institut der Universit\"at M\"unchen, Theresienstr. 39, D-80333 M\"unchen}
\email{avlavrenov at gmail.com}

@@

\begin{theorem*} Suppose $A$ is a local ring with maximal ideal $M$. Then for any $\ell \geq 7$ and $2 \in A^*$ the following commutative square is a pullback in which all arrows are injective:
 \begin{equation} \nonumber
  \xymatrix{ \St(\rD_\ell, A) \ar[r] \ar[d] & \St(\rD_\ell, A[X]) \ar[d] \\ \St(\rD_\ell, A[X\inv]) \ar[r] & \St(\rD_\ell, A[X, X\inv]).}
 \end{equation}
\end{theorem*}

\section{Preliminaries}
%$\langle \alpha, \beta \rangle = (\alpha, \beta^\vee) = (\alpha, \frac{2\beta}{(\beta, \beta)})$ Our convention for Cartan matrices is $A_{ij} = \langle \alpha_i, \alpha_j \rangle = (\alpha_i, \alpha_j^\vee)$.

\subsection{Steinberg groups}
Let $\Phi$ be a reduced and irreducible root system of rank $\geq 2$ and $R$ be a commutative ring with $1$. Recall that in this case the \emph{Steinberg group} $\St(\Phi, R)$ can be defined by means of generators $x_{\alpha}(s)$ 
%(where $\alpha\in\Phi, s\in R$)
and relations:
\begin{align}
& \phantom{[}
x_\alpha(s) \cdot x_\alpha(t) = x_\alpha(s+t),\ \alpha\in\Phi,\ s,t\in R; \label{rel:add}\\
& [x_\alpha(s), x_\beta(t)] = \prod\limits_{i,j\in\mathbb{N}}
 x_{i\alpha + j\beta}\left(N_{\alpha,\beta ij}\, s^i t^j\right),\quad \alpha,\beta\in\Phi,\ \alpha\neq\pm\beta,\ s,t\in R. \label{rel:CCF}
\end{align}
The indices $i$, $j$ appearing in the right-hand side of the above relation range over
all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
The constants $N_{\alpha \beta i j}$ appearing in the right-hand side of \eqref{rel:CCF} are integers equal to $\pm 1,\pm 2,\pm 3$, they are called the {\it structure constants} of the Chevalley group $G_{sc}(\Phi, R)$. Several different methods have been proposed for choosing signs of these constants, see e.\,g.~\cite{V00}, \cite[\S~9]{VP}.

Whenever we speak of the Steinberg group $\St(\Psi, R)$ parametrized by a root subsystem $\Psi \subset \Phi$ we imply that the choice of structure constants 
 for $\St(\Psi, R)$ is compatible with that for $\St(\Phi, R)$ (i.\,e. the obvious map between these groups induced by the embedding $\Psi\subseteq \Phi$ is well-defined).

In this paper we will be mostly interested in the case when the Dynkin diagram of $\Phi$ is {\it simply-laced}, i.\,e. does not contain double bonds. In this case the defining relations of $\St(\Phi, R)$ have the following simpler form:
\begin{align}
&x_{\alpha}(a)\cdot x_{\alpha}(b)=x_{\alpha}(a+b), \tag{R1}\\
&[x_{\alpha}(a),\,x_{\beta}(b)]=x_{\alpha+\beta}(N_{\alpha\beta} \cdot ab),\text{ for }\alpha+\beta\in\Phi, \tag{R2} \\
&[x_{\alpha}(a),\,x_{\beta}(b)]=1,\text{ for }\alpha+\beta\not\in\Phi\cup0. \tag{R3}
\end{align}
In the above formulae $a, b \in R$ and the integers $N_{\alpha, \beta} = N_{\alpha, \beta, 1, 1} = \pm 1$ are the structure constants of the Lie algebra of type $\Phi$. Although there is still some degree of freedom in their choice, these constants always must satisfy the relations, provided by the following lemma (cf.~\cite[\S~14]{VP}). 
\begin{lemma} Suppose $\Phi$ is simply laced and $\alpha, \beta$ are roots of $\Phi$ such that $\alpha+\beta\in \Phi$, then holds
\begin{equation} \label{eq:simplest} N_{\alpha, \beta} = -N_{\beta,\alpha} = - N_{-\alpha, -\beta} = N_{\beta, -\alpha-\beta} = N_{-\alpha-\beta, \alpha}. \end{equation}
If, moreover, $\gamma \in \Phi$ is such that $\alpha,\beta,\gamma$ form a basis of a root subsystem of type $\rA_3$ then holds
\begin{equation} \label{eq:cocycle} N_{\beta,\gamma} \cdot N_{\alpha, \beta+\gamma} = N_{\alpha+\beta, \gamma} \cdot N_{\alpha, \beta}. \end{equation} \end{lemma}
In our computations we will be using the identity~\eqref{eq:simplest} without explicit reference.

@@

\subsection{\texorpdfstring{$\K_2$}{K2}-groups and symbols} In our computations we use two families of explicit elements of $\K_2(\Phi, R)$ called {\it Steinberg and Dennis--Stein symbols}. Notice that our notational conventions for symbols follow~\cite{DS73} and not more modern textbooks such as~\cite{Kbook}. Recall that Steinberg symbols are defined for arbitrary $s, t \in R^\times$ as follows:
\begin{equation} \label{eq:steinberg} \{ s, t \}_\alpha = h_\alpha(st) \cdot h_\alpha^{-1}(s) \cdot h_\alpha^{-1}(t). \end{equation}
In turn, Dennis--Stein symbols are defined for arbitrary $a, b\in R$ satisfying $1 + ab \in R^\times$:
\begin{equation} \label{eq:dennis-stein}  \langle a,b \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- b}{1 + ab}\right) \cdot x_{\alpha}(a) \cdot x_{-\alpha}(b) \cdot x_{\alpha}\left(\tfrac{- a}{1+ab}\right) \cdot h_{\alpha}^{-1}(1 + ab). \end{equation} 
Dennis--Stein symbol $\langle a, b \rangle_\alpha$ can be expressed through Steinberg symbols in the special case when either $a$ or $b$ is an invertible element of $R$. More specifically, the following formulae hold (cf.~\cite[p.~250]{DS73}).
\begin{equation} \label{DS-S-relationship} \langle a, b \rangle_\alpha = \{-a, 1+ab\}_\alpha\text{ for } a, 1+ab\in R^\times,\ \
 \{ s, t \}_\alpha = \left\langle -s, \tfrac{1 - t}{s} \right\rangle_\alpha\text{ for } s, t\in R^\times. \end{equation}
%Using~\eqref{eq:conj-h-h} it is easy to verify that \[[h_\alpha(s), h_\beta(t)] = \{s, t^{\langle \alpha, \beta \rangle}\}_\alpha = \{t, s^{\langle \beta, \alpha \rangle}\}_\beta^{-1}.\] 
Steinberg and Dennis--Stein symbols depend only on the length of $\alpha$, in particular they do not depend on $\alpha$ if $\Phi$ is simply-laced. If $\Phi$ happens to be {\it nonsymplectic}, i.\,e. $\Phi \neq \rA_1, \rB_2, \rC_{\geq 3}$, Steinberg symbols are antisymmetric and bimultiplicative, i.\,e. they satisfy the following identities: \begin{equation} \label{eq:symbol-properties} \{ u, st \} = \{ u, s\} \{ u, t \}, \ \{ u, v \} = \{ v, u\}^{-1}. \end{equation}
For these and other properties of symbols we refer the reader to~\cite{DS73}.

@@

\subsection{Relative Steinberg groups and unstable K-groups} \label{sec:quillen}
In this subsection we recall the definitions and basic facts pertaining to the theory of relative extensions developed by J.-L.~Loday in~\cite{Lo78}. This theory was applied by J.~Loday to the stable Steinberg group $\St(R)$ from algebraic K-theory. The main goal of this subsection is to show that Loday's theory can be applied to unstable Steinberg groups, and that the resulting relative Steinberg groups enjoy the same good properties as their stable counterparts.
Some of the results of this subsection have been briefly mentioned in~\cite{S15} (cf. e.\,g. Corollaries 3--4).

@@

Now let us give an example of the triple $(G, P, S)$ playing a key role in the present paper.
We denote by $\mathrm{O}_{2n}(R)$ and $\mathrm{EO}_{2n}(R)$ the orthogonal group of rank $n$ over a ring $R$ and its elementary subgroup, respectively
 (see e.\,g.~\cite{Su82} for the definition of these groups).
Now set $G_n = \mathrm{O}_{2n}(-)$, $P_n = \mathrm{EO}_{2n}(R)$, $S_n = \St(\rD_n, -)$ and let $\pi$ be the obvious projection $S_n \to P_n$.

@@

\section{Proof of the first part of the injectivity theorem} \label{firstPart}
We start this section by recalling basic notation and facts pertaining to Grothendieck--Witt groups.
%First of all, recall that the stable orthogonal K-groups $\KO_i(R) = \KO_i(\infty, R)$ are precisely the hermitian K-groups ${}_{-1}\!L_i(R)$ introduced by Karoubi in~\cite{Ka80}. We will need yet another redesignation for these groups $\KO_i(R)$, which comes from the theory of {\it higher Grothendieck--Witt groups of schemes}.
Recall that this theory, developed by M.~Schlichting, is a modern broad generalization of the classical hermitian K-theory of rings developed in~\cite{Ka80}. We refer the reader to~\cite[\S~2]{FRS12} and~\cite[\S~2]{AF17} for an introduction to it.

For our purposes it suffices to restrict attention to the affine case, in which  the Grothendieck--Witt groups $\GW_i^{[k]}(R)$ for $i \geq 1,\ [k] \in \ZZ/4\ZZ$ can be considered simply as a shorthand for the following groups:
\begin{equation*} \GW_i^{[k]}(R) = \left\{\begin{array}{ll} \KO_i(R), & k = 0 \\ U_i(R), & k = 1 \\ \mathrm{KSp}_i(R), & k = 2 \\ {}_{-1}\!U_i(R), & k = 3. \end{array}\right. \end{equation*}
Here the groups $\mathrm{KO}_i(R)$ are the stable analogues of the groups $\KO_i(2n, R)$ considered in the previous chapter. Similarly, one can also define the symplectic $K$-groups $\mathrm{KSp}_i(R)$. The groups ${}_{\pm 1}\!U_i(R)$ are defined in~\cite{Ka80} and we will not use their definition directly.

The following result, which is a special case of~\cite[Theorem~9.13]{Sch16} of M.~Schlichting, plays a key role in the proof of~\cref{thm41}.
\begin{theorem*}[Bass Fundamental Theorem]\label{bass-ft} Suppose that $R$ is a regular ring such that $2 \in R^*$, 
then for any $i\geq 1$, $k\in \ZZ/4\ZZ$ there is a natural split exact sequence of abelian groups \[ \xymatrix{ 0 \ar[r] & \GW_i^{[k]}(R) \ar[r] & \GW_i^{[k]}(R[X, X^{-1}]) \ar[r]  & \GW_{i-1}^{[k-1]}(R) \ar[r] & 0.} \] \end{theorem*}
%\begin{proof} This is a very special case of and the remark that follows it. \end{proof}
We will use the above theorem only in the special case $i=0$, in which it boils down to an earlier result of Hornbostel, see~\cite[Corollary~5.3]{Ho05}.

@@

It is obvious that $K(A[X], M[X])$ contains the subgroup $\overline{\St}(\Phi, A[X], XM[X])$. It turns out that, although being larger than this subgroup, $K(A[X], M[X])$ contains very few extra generators, which can all be explicitly described (see~\cref{Kgen} and the corollary that follows it).

It follows from~\cref{Kdecomp1} below that $K(A[X], M[X])$ coincides with the double commutator subgroup $[\overline{\St}(\Phi, A[X], M[X]), \overline{\St}(\Phi, A[X], XA[X])].$ Thus, if we replace relative Steinberg groups in the statement of~\cref{Kgen} with relative elementary groups then the resulting assertion becomes a special case of a much more general recent result of N.~Vavilov and Z.~Zhang (cf.~\cite[Theorem~1]{VZ18}).

Since $ev_{X=0}^*$ admits a section, we can consider $\overline{\St}(\Phi, A, M)$ and $\St(\Phi, M)$ as subgroups of $\overline{\St}(\Phi, A[X], M[X])$,
 moreover, one has $\overline{\St}(\Phi, A[X], M[X]) = \overline{\St}(\Phi, A, M) \cdot K(A[X], M[X]).$
\begin{lemma} \label{Kdecomp1} The following decomposition holds
 \[ K(A[X], M[X]) = \overline{\St}(\Phi, A[X], XM[X]) \cdot \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right].\] \end{lemma}
\begin{proof} Fix $g \in K(A[X], M[X])$ and write it as $g(X) = \prod_i z_{\alpha_i}(f_i(X), \xi_i(X))$ for some $f_i(X) = f_i(0) + Xf_i'(X) \in M[X]$, $\xi_i(X) = \xi_i(0) + X\xi_i'(X) \in A[X]$.
 It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the element $g(X)$ is congruent to $g_1(X) = \prod_i z_{\alpha_i}(f_i(0), \xi_i(X)).$
